---
title: "COVID-19 Contact Tracing Report"
always_allow_html: true
output:
  rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_depth: 2
    toc_float: yes
  officedown::rpptx_document:
    reference_doc: pptx_alternative.pptx
    slide_level: 2
  pagedreport::paged_windmill:
    logo: "logo.svg"
    front_img: "front_img.jpg"
    img_to_dark: TRUE
    logo_to_white: TRUE
  officedown::rdocx_document:
    reference_docx: docx_template.docx
    toc: yes
mainfont: Avenir
geometry: left=2cm,right=2cm,top=2.5cm,bottom=2cm
params:
  rendered_by_shiny: false
  todays_date: NA
  contacts_df_long: NA
  report_format: NA
#knit: pagedown::chrome_print
google-font: TRUE
main-font: "Open Sans"
fontsize: 10pt
main-color: "#3391CF"
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi = 300)

source(here::here("global.R"))
source(here("helper_scripts/misc_functions.R")) ## redundant?
source(here::here("helper_scripts/server_functions.R"))


number_of_chunks <- 19
current_chunk <- 0

update_rmd_progress <- function(){
  if (params$rendered_by_shiny) {
  current_chunk <<- current_chunk + 1
  shiny::setProgress(current_chunk/number_of_chunks, 
                     detail = paste0("Building section ", 
                                      current_chunk, 
                                      " of ", 
                                      number_of_chunks ))
  }
  
  if(current_chunk == number_of_chunks){
    
     shiny::setProgress(1, 
                        detail = "Finalizing report"
                        )
    
  }
  
}

## turn off highcharter animations
newtheme <-
  hc_theme_merge(
    getOption("highcharter.theme"),
    hc_theme(plotOptions = list(series = list(animation = FALSE)),
             exporting = list(buttons = list(contextButton = list(menuItems = myMenuItems))))

    )
  

options(highcharter.theme = newtheme)


update_rmd_progress()
```


```{css}
h1 {
  text - align:center
}
body {
  background - color:#f0f2fa
}

.tab - content{
  margin - bottom:70px
}
```



```{r}
## if we are knitting outside of shiny, we cannot rely on reactives.
## Thus, we run the functions manually
## At the end, we will output the cleaned dataframe for visualization

if (params$rendered_by_shiny == FALSE){
  
  report_format <- "html"
  data_to_use <-  "Use preloaded data"
  preloaded_data_choice <- "Sample tracing data"
  select_region <- "Abidjan 1"
  todays_date <- Sys.Date()
  
  source(here("helper_scripts/server_functions.R")) # only here to facilitate manual app work
  
  # ~~~~ read_file_raw ----
  
   tracing_data_raw <-
    read_file_raw(
      data_to_use = data_to_use,
      preloaded_data_options = preloaded_data_options,
      preloaded_data_choice = preloaded_data_choice)
  
  # ~~~~ read_file_transformed ----
  
  contacts_df_long_transformed <- 
    read_file_transformed(
      tracing_data_raw = tracing_data_raw
      )
  
# ~~~~ read_file_transformed_regional ----  ## probably will make a separate Rmd for regional report

  contacts_df_long_transformed_regional <- 
    read_file_transformed_regional(
      contacts_df_long_transformed = contacts_df_long_transformed, 
      select_region = select_region
      )
  
# ~~~~ read_file_filtered ----
  
  contacts_df_long <- 
    read_file_filtered(
      contacts_df_long_transformed = contacts_df_long_transformed,
      todays_date = todays_date,
      legend_df = legend_df
    )

# ~~~~ read_file_filtered_regional ----  ## probably will make a separate Rmd for regional report

    contacts_df_long_regional <- 
    read_file_filtered_regional(
      contacts_df_long_transformed = contacts_df_long_transformed,
      todays_date = todays_date,
      legend_df = legend_df
    )
    
}
  
update_rmd_progress()
```

```{r}

## if knitting within shiny
if (params$rendered_by_shiny == TRUE){
contacts_df_long <- params$contacts_df_long
todays_date <- params$todays_date
report_format <- params$report_format
}


chunk_results <- switch(report_format, 
                        "shiny" = NULL,
                        "html" = NULL,
                        ## hide annoying grid arrange output. Only the static formats need this hidden
                        "pdf" = "hide", 
                        "docx" = "hide",
                        "pptx" = "hide")
                        

update_rmd_progress()
```


```{r}
Country <- "Cotê d'Ivoire"
min_date <- min(na.omit(contacts_df_long$follow_up_date))
max_date <- max(na.omit(contacts_df_long$follow_up_date))
```


# VALUE BOX SUMMARIES

```{r, fig.width=3.5, fig.height=2, out.width="48%"}

contacts_per_day_value_box(contacts_df_long,
                           todays_date) %>%
  .$ggplot_valuebox


cumulative_contacts_value_box(contacts_df_long,
                              todays_date) %>%
  .$ggplot_valuebox

update_rmd_progress()
```


```{r, fig.width=3.5, fig.height=2, out.width="48%"}

contacts_under_surveillance_value_box(contacts_df_long,
                                      todays_date) %>%
  .$ggplot_valuebox

pct_contacts_followed_value_box(contacts_df_long,
                                      todays_date) %>%
  .$ggplot_valuebox


update_rmd_progress()
```


# DATA PERTAINING TO ALL CONTACTS {.unlisted .unnumbered}

# Regional breakdown

## {.unlisted .unnumbered}

```{r, results = "asis"}
all_contacts_per_region_text(contacts_df_long,
                               todays_date,
                               report_format)

update_rmd_progress()
```


## Regional breakdown bar chart

```{r}
all_contacts_per_region_bar_chart(contacts_df_long,
                                      todays_date,
                                      report_format)
update_rmd_progress()
```

## Regional breakdown sunburst plot

```{r}
all_contacts_per_region_sunburst_plot(contacts_df_long,
                                      todays_date,
                                      report_format)
update_rmd_progress()
```

## Regional breakdown table

```{r}

all_contacts_per_region_table(contacts_df_long,
                              todays_date,
                              report_format)
update_rmd_progress()
```

<!-- # ~~~ app_tab_row_2 ---- -->


# Regional trends

## {.unlisted .unnumbered}

```{r, results = "asis"}
contacts_under_surveillance_per_region_over_time_text(contacts_df_long,
                                                      todays_date,
                                                      report_format)
update_rmd_progress()
```


## Regional trends absolute counts
```{r}
contacts_under_surveillance_per_region_over_time_bar_chart(contacts_df_long,
                                                           todays_date,
                                                           report_format)
update_rmd_progress()
```

## Regional trends relative proportions
```{r}
contacts_under_surveillance_per_region_over_time_bar_chart_relative(contacts_df_long,
                                                                    todays_date,
                                                                    report_format)
update_rmd_progress()
```


<!-- # ~~~ app_tab_row_3 ---- -->

# Contacts per case

## {.unlisted .unnumbered}

```{r, results = "asis"}
total_contacts_per_case_text(contacts_df_long,
                             todays_date,
                             report_format)

update_rmd_progress()
```

## Contacts per case donut plot

```{r}
total_contacts_per_case_donut_plot(contacts_df_long,
                             todays_date,
                             report_format)

update_rmd_progress()
```

## Contacts per case bar chart

```{r}
total_contacts_per_case_bar_chart(contacts_df_long,
                             todays_date,
                             report_format)

update_rmd_progress()
```



# Case-contact relationships

## {.unlisted .unnumbered}

```{r, results = "asis"}
total_contacts_per_link_type_text(contacts_df_long,
                                        todays_date,
                                        report_format)

update_rmd_progress()
```

## Case-contact relationships donut plot

```{r}
total_contacts_per_link_type_donut_plot(contacts_df_long,
                             todays_date,
                             report_format)

update_rmd_progress()
```

## Case-contact relationships bar chart

```{r}
total_contacts_per_link_type_bar_chart(contacts_df_long,
                             todays_date,
                             report_format)

update_rmd_progress()
```

# DATA PERTAINING TO ACTIVE CONTACTS {.unlisted .unnumbered}

# Follow-up timelines

## {.unlisted .unnumbered}

```{r, results = "asis"}
active_contacts_timeline_snake_text(contacts_df_long,
                             todays_date,
                             report_format)
```

## Follow-up timeline snake plot

```{r}
active_contacts_timeline_snake_plot(contacts_df_long,
                             todays_date,
                             report_format)

update_rmd_progress()
```

## Follow-up summary bar chart

```{r}

```


