---
title: "COVID-19 Contact Tracing Report"
always_allow_html: true
output:
  rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_depth: 2
    toc_float: yes
  rmarkdown::slidy_presentation:
    slide_level: 3
  pagedreport::paged_windmill:
    logo: "logo.svg"
    front_img: "front_img.jpg"
    img_to_dark: TRUE
    logo_to_white: TRUE
  officedown::rdocx_document:
    reference_docx: docx_template.docx
    toc: yes
  officedown::rpptx_document:
    reference_doc: pptx_template.pptx
    slide_level: 2
mainfont: Avenir
geometry: left=2cm,right=2cm,top=2.5cm,bottom=2cm
params:
  rendered_by_shiny: false
  todays_date: NA
  contacts_df_long: NA
  report_format: NA
#knit: pagedown::chrome_print
google-font: TRUE
main-font: "Open Sans"
fontsize: 10pt
main-color: "#3391CF"
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi = 300)


number_of_chunks <- 22
current_chunk <- 0

update_rmd_progress <- function(){
  if (params$rendered_by_shiny) {
  current_chunk <<- current_chunk + 1
  shiny::setProgress(current_chunk/number_of_chunks, 
                     detail = paste0("Building section ", 
                                      current_chunk, 
                                      " of ", 
                                      number_of_chunks ))
  }
  
  if(current_chunk == number_of_chunks){
    
     shiny::setProgress(1, 
                        detail = "Finalizing report"
                        )
    
  }
  
}

## turn off highcharter animations
library(highcharter)

myMenuItems <-
  c(
    "printChart",
    "separator",
    "downloadPNG",
    "downloadJPEG",
    "downloadPDF",
    "downloadSVG",
    "separator",
    "viewData",
    "downloadCSV",
    "downloadXLS"
  )

newtheme <-
  hc_theme_merge(
    getOption("highcharter.theme"),
    hc_theme(plotOptions = list(series = list(animation = FALSE)),
             exporting = list(buttons = list(contextButton = list(menuItems = myMenuItems))))

    )
  

options(highcharter.theme = newtheme)


update_rmd_progress()
```


```{css}
h1 {
  text - align:center
}
body {
  background - color:#f0f2fa
}

.tab - content{
  margin - bottom:70px
}
```



```{r paramsSetNonShiny}
## if we are knitting outside of shiny, we cannot rely on reactives.
## Thus, we run the functions manually
## At the end, we will output the cleaned dataframe for visualization

if (params$rendered_by_shiny == FALSE){
  

  output <- list()
  input <- list()
  
  source(here::here("global.R"))
  source(here::here("helper_scripts/server_functions.R")) 


  
  input$data_to_use <- "Use preloaded data"
  preloaded_data_options <-  preloaded_data_options ## defined in global file
  input$preloaded_data_choice <- "Sample tracing data"
  cols_to_exclude_from_filters <- c("placeholder_non_column")
  input$uploaded_data_contacts_list$datapath <-
    here::here("data/Formulaire_Identification_contact_CIV_-_latest_version_-_labels_-_2021-02-20-13-17-18.xlsx")
  input$uploaded_data_follow_up_list$datapath <-
    here::here("data/Formulaire_Suivi_contacts_CIV_-_latest_version_-_labels_-_2021-02-20-14-25-48.xlsx")
  report_format <- "html (page)"

  if (input$data_to_use == "Use preloaded data")   input$select_date_of_review <- as.Date("2021-04-13")
  if (input$data_to_use == "Use uploaded data")   input$select_date_of_review <- as.Date("2021-02-20")
  
  todays_date <- input$select_date_of_review
  
      


  # ~~~~ read_file_raw ----
  
   tracing_data_raw <-
    read_file_raw()
  
  # ~~~~ read_file_transformed ----
  
  contacts_df_long_transformed <- 
    read_file_transformed(tracing_data_raw = tracing_data_raw)
  
  
# ~~~~ read_file_filtered ----
  
  contacts_df_long <- 
    read_file_filtered(contacts_df_long_transformed,
                       input$select_date_of_review)

}
  
update_rmd_progress()
```


```{r paramsSetShiny}

## if knitting within shiny
if (params$rendered_by_shiny == TRUE){
  source(here::here("global.R"))
  source(here::here("helper_scripts/server_functions.R")) 

contacts_df_long <- params$contacts_df_long
todays_date <- params$todays_date
report_format <- params$report_format
}


update_rmd_progress()
```


# VALUE BOX SUMMARIES

```{r valueBoxes1, fig.width=3.5, fig.height=2, out.width="48%"}

contacts_per_day_value_box(contacts_df_long,
                           todays_date,
                           report_format)


cumulative_contacts_value_box(contacts_df_long,
                              todays_date,
                              report_format)

update_rmd_progress()
```


```{r valueBoxes2, fig.width=3.5, fig.height=2, out.width="48%"}

contacts_under_surveillance_value_box(contacts_df_long,
                                      todays_date,
                                      report_format)

pct_contacts_followed_value_box(contacts_df_long,
                                todays_date,
                                report_format)


update_rmd_progress()
```


# OUTPUTS PERTAINING TO ALL CONTACTS {.unlisted .unnumbered}

# Admin level 1 breakdown

## {.unlisted .unnumbered}

```{r allContactsPerAdmin1Text, results = "asis"}
all_contacts_per_admin_1_text(contacts_df_long,
                               report_format)

update_rmd_progress()
```


### Admin level 1 breakdown bar chart

```{r allContactsPerAdmin1BarChart}
all_contacts_per_admin_1_bar_chart(contacts_df_long,
                                   report_format)

update_rmd_progress()
```

### Admin level 1 breakdown sunburst plot

```{r allContactsPerAdmin1SunburstPlot}
all_contacts_per_admin_1_sunburst_plot(contacts_df_long,
                                      report_format)

update_rmd_progress()
```

### Admin level 1 breakdown table

```{r allContactsPerAdmin1Table}
all_contacts_per_admin_1_table(contacts_df_long,
                              report_format)

update_rmd_progress()
```

<!-- # ~~~ main_tab_row_2 ---- -->


# Admin level 1 trends

## {.unlisted .unnumbered}

```{r contactsUnderSurveillancePerAdmin1OverTimeText, results = "asis"}
contacts_surveilled_admin_1_text(contacts_df_long,
                                 todays_date,
                                 report_format)
update_rmd_progress()
```


### Admin level 1 trends, absolute counts
```{r contactsUnderSurveillancePerAdmin1OverTimeBarChart}
contacts_surveilled_admin_1_bar_chart(contacts_df_long,
                                      todays_date,
                                      report_format)
update_rmd_progress()
```

### Admin level 1 trends, relative proportions
```{r contactsUnderSurveillancePerAdmin1OverTimeBarChartRelative}
contacts_surveilled_admin_1_bar_chart_relative(contacts_df_long,
                                               todays_date,
                                               report_format)
update_rmd_progress()
```


<!-- # ~~~ main_tab_row_3 ---- -->

# Contacts per case

## {.unlisted .unnumbered}

```{r totalContactsPerCaseText, results = "asis"}
total_contacts_per_case_text(contacts_df_long,
                             report_format)

update_rmd_progress()
```


### Contacts per case table

```{r totalContactsPerCaseTable}
total_contacts_per_case_table(contacts_df_long,
                             report_format)

update_rmd_progress()
```


### Contacts per case donut plot

```{r totalContactsPerCaseDonutPlot}
total_contacts_per_case_donut_plot(contacts_df_long,
                             report_format)

update_rmd_progress()
```

### Contacts per case bar chart

```{r totalContactsPerCaseBarChart}
total_contacts_per_case_bar_chart(contacts_df_long,
                             report_format)

update_rmd_progress()
```



# Case-contact relationships

## {.unlisted .unnumbered}

```{r totalContactsPerLinkTypeText, results = "asis"}
total_contacts_per_link_type_text(contacts_df_long,
                                        report_format)

update_rmd_progress()
```

### Case-contact relationships donut plot

```{r totalContactsPerLinkTypeDonutPlot}
total_contacts_per_link_type_donut_plot(contacts_df_long,
                             report_format)

update_rmd_progress()
```

### Case-contact relationships bar chart

```{r totalContactsPerLinkTypeBarChart}
total_contacts_per_link_type_bar_chart(contacts_df_long,
                             report_format)

update_rmd_progress()
```

# OUTPUTS PERTAINING TO ACTIVE CONTACTS {.unlisted .unnumbered}

# Follow-up timelines

## {.unlisted .unnumbered}

```{r activeContactsTimelineText, results = "asis"}
active_contacts_timeline_text(contacts_df_long,
                             todays_date,
                             report_format)
```

### Follow-up summary bar chart

```{r activeContactsBreakdownBarChart, fig.width = 7, dpi = if(report_format %in% c("html (page)", "html (slides)")) {96} else {300} }
active_contacts_breakdown_bar_chart(contacts_df_long,
                           todays_date,
                           report_format,
                           legend_df)

update_rmd_progress()

```

### Follow-up timeline snake plot

```{r activeContactsTimelineSnakePlot, fig.width = 7, dpi =  if(report_format %in% c("html (page)", "html (slides)")) {96} else {300} }
active_contacts_timeline_snake_plot(contacts_df_long,
                           todays_date,
                           report_format,
                           legend_df)

update_rmd_progress()
```


# Contacts not seen recently

## {.unlisted .unnumbered}

```{r lostContactsLinelistText, results = "asis"}
lost_contacts_linelist_text(contacts_df_long,
                             todays_date,
                             report_format)
update_rmd_progress()
```

### Loss to follow-up, past 3 days

```{r contactsLost24To72HoursTable}
contacts_lost_24_to_72_hours_table(contacts_df_long,
                             todays_date,
                             report_format)
```

### List of contacts not seen

```{r lostContactsLinelistTable, results = "asis"}

lost_contacts_linelist_table(contacts_df_long,
                             todays_date,
                             report_format = report_format) %>%
  .$output_table

```



